The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-23 paper.tex
update

  A crucial component in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  First, pyFC create a dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$ that is clumpy but obeys\
  the log-normal probability distribution\
  %the log-normal probability distribution \citep{Berkhuijsen2008}\
  with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f_{\text{clumpy}}(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\

  The temperature in each cell of the clumpy disk is determined by $p_{\text{disk}}$

  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.

  %The reader is referred to \citet{LA2002} and \citet{Wagner2012} for further details of this method.
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing clumpy structure, and we do not repeat here.

  The temperature in each cell of the warm gas distribution is determined by pressure equilibrium with hot gas.\
  When the warm gas temperature exceeds $T_{\text{crit}}=$ K, it is deemed to be thermally unstable and is replaced\
  by hot gas. This makes the gas porous.

  \begin{enumerate}
     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(\bold{x})$ by \Cref{isothermal-disk-density}.
     \item Using PyFC code to obtain a dimensionless clumpy distribution $f_{\text{clumpy}}$ obeying\
           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
     \item $\rho_{\text{ismDisk}}(\bf{x}) = f_{\text{clumpy}}(\bf{x}) \rho_{\text{isoDisk}}(\bf{x})$.
     \item
  \end{enumerate}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                                    & Description                               & Value                                \\ \midrule
{\bf Static stellar potential }\citep{velocity-dispersion-MW}&                                           &                                      \\
$\sigma_{\text{bulge}}$                                      & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                \\
$\rho_{\text{bulge}}^{\text{peak}}$                          & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ \\ \hline
{\bf Static dark halo potential }\citep{Johnston1995}        &                                           &                                      \\
$v_{\text{halo}}$                                            &                                           & 131.5 km$\cdot$s$^{-1}$              \\
$d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \hline
{\bf Isothermal disk }\citep{peak-ism-density}               &                                           &                                      \\
$z_{0}$                                                      & Scale height of disk                      & 100 pc                               \\
$T_{\text{\text{isoDisk}}}$                                  & Temperature of disk                       & $10^{3}$ K                           \\
$\rho_{\text{isoDisk}}^{\text{peak}}$                        & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         \\ \hline
{\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\ \hline
{\bf Clumpy disk }\citep{Wagner2012}                         &                                           &                                      \\
$T_{\text{\text{c}}}$                                        & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   \\
$k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
$\mu_{\text{clumpy}}$                                        & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 \\
$\sigma_{\text{clumpy}}$                                     & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 \\ % RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES Wagner (2011)
$\beta$                                                      & Power law index                           & -5/3                                 \\ \midrule
\end{tabular}
\end{table*}

>>>>

  A crucial component in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The pyFC randomly generates dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$ that is clumpy and porous.
  The random scalar field obeys the log-normal probability distribution\
  %the log-normal probability distribution \citep{Berkhuijsen2008}\
  with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f_{\text{clumpy}}(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\

  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing clumpy structure, and we do not repeat here.

  Finally, we multiply $f_{\text{clumpy}}(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
  to obtain the density of ISM disk $\rho_{\text{ismDisk}}(\bold{x})$. i.e.\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f_{\text{clumpy}}(\bold{x}) \rho_{\text{isoDisk}}(z)$.

  The temperature in each cell of the disk is determined by pressure equilibrium with hot gas.\

  When the warm gas temperature exceeds $T_{\text{crit}}=$ K, it is deemed to be thermally unstable and is replaced\
  by hot gas. This makes the gas porous.

%  \begin{enumerate}
%     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(z)$ by \Cref{isothermal-disk-density}.
%     \item Using PyFC code to obtain a dimensionless clumpy distribution $f_{\text{clumpy}}$ obeying\
%           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
%     \item \Cref{density-ism-disk}.
%     \item
%  \end{enumerate}

\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                                    & Description                               & Value                                \\ \midrule
{\bf Static stellar potential }\citep{velocity-dispersion-MW}&                                           &                                      \\
$\sigma_{\text{bulge}}$                                      & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                \\
$\rho_{\text{bulge}}^{\text{peak}}$                          & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ \\ \hline
{\bf Static dark halo potential }\citep{Johnston1995}        &                                           &                                      \\
$v_{\text{halo}}$                                            &                                           & 131.5 km$\cdot$s$^{-1}$              \\
$d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \hline
{\bf Isothermal disk }\citep{peak-ism-density}               &                                           &                                      \\
$z_{0}$                                                      & Scale height of disk                      & 100 pc                               \\
$T_{\text{\text{isoDisk}}}$                                  & Temperature of disk                       & $10^{3}$ K                           \\
$\rho_{\text{isoDisk}}^{\text{peak}}$                        & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         \\ \hline
{\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\ \hline
{\bf Clumpy disk }\citep{Wagner2012}                         &                                           &                                      \\
$T_{\text{\text{c}}}$                                        & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   \\
$k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
$\mu_{\text{clumpy}}$                                        & Mean of scalar field                      & 1.0                                  \\
$\sigma_{\text{clumpy}}$                                     & Dispersion of scalar field                & 1.7                                  \\ % RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES Wagner (2011)
$\beta$                                                      & Power law index                           & -5/3                                 \\ \midrule
\end{tabular}
\end{table*}
